---
title       : Uses of Data
subtitle    : in Clinical Quality Measurement
author      : Joshua Hagedorn
job         : tbd
#logo        : tbd-icon-small.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : prettify  # {highlight.js, prettify, highlight}
hitheme     : zenburn       #      
widgets     : []            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r opts_chunk$set(echo=F, message=F , comment=NA)}
```

## Context: Resources
(- $) (+ #) -> (- Redundancy) (+ Value %)

>- Less money
>- More people
>- Reduce redundancy
>- Increase value

--- .class #id 

## Context: Costs in MSHN Region

```{r nvd3plot, results = 'asis', comment = NA, message = F, echo = F}
library(rCharts)

all_cost <- read.csv("C:\\Users\\Josh\\Documents\\GitHub\\presenting\\nccmh_clinical_data\\assets\\all_cost.csv")

allcost <- nPlot(CostInMillions ~ FY, group = "ServiceType", data = all_cost,type = 'stackedAreaChart', id = 'chart')
allcost$xAxis(axisLabel = 'Year', width = 62)
allcost$yAxis(axisLabel = 'Total cost, in millions', width = 62)
#allcost$addControls("y", value = "CostInMillions", values = c("SumOfCost","Cost1kSvd"))
allcost$show('inline')
```

*Data from* [Open404](https://github.com/j-hagedorn/open404)

--- .class #id 

## Context: Variation...

```{r nvd3plot2, results = 'asis', comment = NA, message = F, echo = F}
library(rCharts)

bar_allhosp <- read.csv("C:\\Users\\Josh\\Documents\\GitHub\\presenting\\nccmh_clinical_data\\assets\\bar_allhosp.csv")

h1 <- nPlot(CostPerUnit ~ CMHSP, group = "FirstofService.Description", data = bar_allhosp, type = "multiBarChart", id = "Cost per unit")
h1$xAxis(axisLabel = 'CMHSP', width = 62)
h1$yAxis(axisLabel = 'Cost per day, 2013', width = 62)
h1$chart(color = c('#bdc9e1', '#67a9cf', '#02818a'))
h1$show('inline')
```

*Data from* [Open404](https://github.com/j-hagedorn/open404)

--- .class #id 

## Context: Integration
(- Redundancy) (- Stigma) (+ Science) -> Integration

>- Redundant systems, admin functions

>- Less stigma

>- Innovations in science (genomics,upstream factors,&c.)

--- .class #id 

## Remaking the Public Behavioral Health System

>- Open Knowledge

>- Public System Entrepeneurs

>- Designed to address "wicked" problems

--- .class #id 

## "Wicked" Problems: Characteristics
(*term borrowed from design thinking)

1. No universal definition
2. Improve, not solve
3. Many causes
4. Interconnected
5. No single measure of success

--- .class #id 

## ONLY THE DIFFICULT INSPIRES THE NOBLE-HEARTED 

Can any one person fathom this situation?

>- No.   Enter data.

>- Not a "single source of truth," but a shared situation.

*** =pnotes
Title quote by S. Kierkegaard
System 1 v System 2 
We overestimate the effects of our actions
In unpredictable situations, our inconsistency wrecks validity

--- .class #id 

## Making it useful

What information would you need to make you change the way you live?

>- What's the issue? (Measures, Analysis)
>- What to do? (Levers)
>- What's success? (Target)

--- .class #id 

## FACT IS THE SWEETEST DREAM THAT LABOR KNOWS

* Stigma: When do labels become characteristics?

* Self-tracking as empowerment
([Quantified Self](http://quantifiedself.com/))

* Self-monitoring helps (obesity, bipolar)

* Use of data in a clinical context
([Boswell, et al, 2013](http://www.scottdmiller.com/wp-content/uploads/2014/06/Implementing-routine-outcome-monitoring-in-clinical-practice-Benefits-challenges-and-solutions-Psychotherapy-Research_Boswell-Kraus-Mi.pdf))

* Frequent, consistent 
([Peterson, et al. 2014](http://onlinelibrary.wiley.com/doi/10.1002/oby.20807/full))

--- .class #id 

## To Do List:

* Key Questions
* Identify Levers
* Build Measures
* Get Data
* Analyze Data
* Communication
* Build Data Literacy
* Integrate into Process
* Use Data

--- .class #id 

## Ask Real Questions

Based on contextual themes:
* Quality
* Cost / Resource Use
* Integration / Coordination

--- .class #id

## Data Lab

--- .class #id

## Homework
1. Identify data points currently measured which are relevant for you in your role.
2. Identify 2 ways that you could usefully integrate data into your clinical practice (e.g. supervision, pre-PCP meetings, etc.)

--- .class #id

<style> 
.title-slide {
  background-color: #ffffff; /* #EDE0CF; ; #CA9F9D*/
  /* background-image:url(http://goo.gl/EpXln); */
} 
</style>
